Inferring neural networks from fluorescent calcium imaging using partial correlation and sample weighting

### 2014-06-06 article.tex
wording

Cutting edge optical devices [todo cite] allows to track simultaneously
the neural activity of thousands of neurons through the fluorescent
calcium indicator.
From those observational data, the neural connectivity inference consists in
highlighting direct relationships between neurons. However, those imaging
systems have a sampling rate smaller than the neuron firing speed and are
limited only two dimensional image, which may lead to superpose the activity
of different neurons. Furthermore, the decay of the fluorescent calcium signal
is slow compare to its rise.

>>>>

Cutting edge optical devices [todo cite] allows to track simultaneously
the neural activity of thousands of neurons through a fluorescent
calcium indicator.
From those observational data, the neural connectivity inference consists in
highlighting direct relationships between neurons. However, those imaging
systems have a sampling rate smaller than the neuron firing speed and are
limited to two dimensional image, while the neuronal network is three dimensional
structure, which may lead to superpose the observed activity
of different neurons. Furthermore, the decay of the fluorescent calcium signal
is slow compare to its rise.
